Bird beak's elaboration and exploration: data preparation

### 2021-09-21 Analysis/01-Data_preparation.Rmd
Save the groups

## Reading the clades list
groups_level1 <- make.level.list(clades_list, level = 1, threshold = 20)
groups_level2 <- make.level.list(clades_list, level = 2, threshold = 20)
all_groups <- c(groups_level1$list, groups_level2$list)
```

>>>>

## Reading the clades list
groups_level1 <- make.level.list(clades_list, level = 1, threshold = 20)
groups_level2 <- make.level.list(clades_list, level = 2, threshold = 20)
all_groups <- c(groups_level1$list, groups_level2$list)
group_names_level_1_2 <- all_groups
save(group_names_level_1_2, file = "../Data/Processed/group_names_level_1_2.rda")
```
